---
title: "DEG_T"
author: "Zhu Ni"
date: "`r Sys.Date()`"
output: html_document
---

# Load Data
```{r}
library(Seurat)
library(RcppML)
library(irGSEA)
library(fgsea)
library(data.table)
library(ggplot2)
library(dplyr)
library(msigdb)
library(GSEABase)
library(ggplot2)

sce_Tcell_TCR <- readRDS("./tmp/sc_Tcell_TCR.rds")
Idents(sce_Tcell_TCR) <- "RNA_snn_res.0.6"
```

# Subset
```{r}
clusters <- c("1","2")
clonesize <- c("Large (0.01 < X <= 0.1)", "Medium (0.001 < X <= 0.01)")
meta.list <- list()
sce_sub_Tcell.list <- list()

for (cluster in clusters){
  print(cluster)
  meta.list[[cluster]] <- subset(sce_Tcell_TCR@meta.data, RNA_snn_res.0.6 %in% cluster & cloneSize %in% clonesize)
  sce_sub_Tcell.list[[cluster]] <- sce_Tcell_TCR[, colnames(sce_Tcell_TCR) %in% rownames(meta.list[[cluster]])]
}
```

# irGSEA
```{r}
result.dge.list <- list()
for (cluster in clusters) {
  print(cluster)
  sce_sub_Tcell.list[[cluster]] <- irGSEA.score(object = sce_sub_Tcell.list[[cluster]],assay = "RNA",
                             slot = "counts", seeds = 42, ncores = 1,
                             min.cells = 3, min.feature = 0,
                             custom = F, geneset = NULL, msigdb = T,
                             species = "Homo sapiens", category = "H",
                             subcategory = NULL, geneid = "symbol",
                             method = c("AUCell","UCell","singscore"),
                             aucell.MaxRank = NULL, ucell.MaxRank = NULL,
                             kcdf = 'Gaussian')
  result.dge.list[[cluster]] <- irGSEA.integrate(sce_sub_Tcell.list[[cluster]],
                                                 group.by = "group",
                                                 method = "AUCell",
  )
  }
saveRDS(result.dge.list, "../Projects/results/irGSEA/result.dge.list_CASH_Normal.rds")
```

# Barplot
``````{r}
top10.list <- list()
plot.list <- list()
clusters <- c("1","2")
for (cluster in clusters) {
  top10_up <- result.dge.list[[cluster]]$AUCell %>%
    filter(cluster == "CASH") %>% 
    filter(direction == "up") %>%
    arrange(desc(avg_diff)) %>%
    head(10)
  
  top10_down <- result.dge.list[[cluster]]$AUCell %>%
    filter(cluster == "CASH") %>% 
    filter(direction == "down") %>%
    arrange(desc(avg_diff)) %>%
    head(10)
  
  top10_combined <- bind_rows(top10_up, top10_down)
  
  top10_combined <- top10_combined %>%
    mutate(log10p = -log10(abs(avg_diff)),
           annotation = direction)
  top10_combined$log10p <- ifelse(top10_combined$direction == "up", 
                                  top10_combined$log10p, 
                                  top10_combined$log10p * -1)
  top10_combined <- top10_combined %>%
    mutate(Name = stringr::str_wrap(Name, width = 20))
  top10.list[[cluster]] <- top10_combined
  #ggplot
  plot.list[[cluster]] <- ggplot(top10.list[[cluster]]) +
    geom_bar(aes(x = reorder(Name, log10p), y = log10p, fill = annotation),
             stat = "identity", color = "white") +
    geom_text(aes(x = reorder(Name, log10p), y = 0, label = Name),
              size = 7 * 0.35, angle = 0) +
    # hjust = ifelse(top10_combined$log10p > 0, -0.1, 1.1)) + 
    scale_fill_manual(name = "", values = c("down" = "#0f7b9f", "up" = "#d83215")) +
    coord_flip() +
    cowplot::theme_cowplot() +
    theme(
      axis.text.x = element_text(size = 7),
      text = element_text(size = 7),
      axis.line = element_line(size = 0.3),
      axis.ticks = element_line(size = 0.3),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.line.y = element_blank(),
      panel.border = element_blank(),
      legend.position = "right") +
    labs(x = "", y = "-log10(avg_diff)", 
         title = paste("Top 10 Upregulated and Downregulated Pathways in CASH_cluster", cluster))
}

for (cluster in clusters) {
  print(plot.list[[cluster]])
}

cluster1 <- table(sce_sub_Tcell.list[[1]]@meta.data$cloneSize, sce_sub_Tcell.list[[1]]@meta.data$group)
cluster2 <- table(sce_sub_Tcell.list[[2]]@meta.data$cloneSize, sce_sub_Tcell.list[[2]]@meta.data$group)
print(cluster1)
print(cluster2)
```

